---
title: "STAT 385 - Homework 6"
author: "Jayhwan Lee - jayhwan2"
date: "Due 11:59 PM, 3/30/2020"
output:
  html_document:
    df_print : paged
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***

## Submit your homework

Make sure you check the following requirements when submitting your homework:

- Put your name - your NetID as the author info at the top of the Rmd file.
- After pushing the latest commit to Git, check if the changes are reflected on [github.com](https://github.com/).
  - DO NOT directly upload to github.com! That is not how we push a commit in this class!

Failure to meet the above requirements will negatively impact your grade.

***

## Before you start

- **For all plots in this homework, you have to use the functions from the ggplot2 package**.
  - If you use base R plotting functions, your answers will NOT be graded.
- The maximum possible points for this homework is 70.
  - Make sure you answer all the questions!

***

## Dataset: diamonds from the ggplot2 package

The ggplot2 package include many interesting datasets. We looked at `mpg` in lecture this week. Now, we will explore the `diamonds` dataset. This data contains the prices and other attributes of almost 54,000 diamonds.

```{r message=FALSE}
library(tidyverse)
str(diamonds)
library(ggplot2)
```

- Run `?diamonds` to know what each variable presents.

### Scatterplot

- There are 4 parts to this exercise: each part worths 5 points.

- **(a)** Graph a scatterplot of `price` vs `carat`.
  - `price` as the $y$-axis and `carat` as the $x$-axis.
  
```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_point(mapping = aes(x = carat, y = price)) 

```

- **(b) With the above graph**, adjust the transparency level of ALL the points so we can see clearly where the clusters are:

```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_point(mapping = aes(x = carat, y = price, alpha = .2))

```

- **(c) Now create a new plot**, graph a scatterplot of `price` vs `carat`, and color the points BY the quality of the cut (`cut`)!
  - Don't change the transparency level of the points.

```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_point(mapping = aes(x = carat, y = price, alpha = .2, color = cut))

```

- **(d) What can you conclude based on the above graph?**
  - **ANSWER:**     
$\rightarrow$ First of all, we can vividly see that as the weigth (carat) of the diamond gets heavier the price increases. Moreover, as the quality of the cut goes from fair to ideal, the price of the diamond increases.
  
### Boxplot

- There are 3 parts to this exercise: each part worths 5 points.

- **(a)** Graph a boxplot of `carat` vs `cut`.
  - `carat` as the $y$-axis and `cut` as the $x$-axis.
  
```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = cut, y = carat))

```

- **(b) With the plot above**, rotate it so `cut` is on the $y$-axis and `carat` is on the $x$-axis.
  - Make sure the plot is still a boxplot.
  
```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = carat, y = cut))

```

- **(c) With the plot from (b)**, color the boxplot dark blue.

```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = carat, y = cut), color = "darkblue")

```

### Histogram

- There are 3 parts to this exercise: each part worths 5 points.

- **(a)** Graph a histogram of `price`.
  
```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_histogram(mapping = aes(price))

```

- **(b) With the plot above**, color the bars dark orange.
  
```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_histogram(mapping = aes(price), color = "darkorange", fill = "darkorange")

```

- **(c) With the plot from (b)**, change the number of bins to 50.

```{r fig.align='center'}

ggplot(data = diamonds) +
  geom_histogram(bins = 50, mapping = aes(price), color = "darkorange", fill = "darkorange")

```



***

## Dataset: 2015 Flight Delays and Cancellations Data

In this exercise, we continue to work with the 2015 Flight Delays and Cancellations Data provided by the U.S. Department of Transportation. This is a huge dataset availalbe on [Kaggle](https://www.kaggle.com/usdot/flight-delays#airports.csv). But for us, we will only take a look at flights **flying out** from O'Hare International Airport (ORD) in January, 2015.

### Load data

- I have filtered out the data specific to O'Hare and stored it in `ohare_jan.csv`. This filtered data is available at the URL: https://nkha149.github.io/stat385-sp2020/files/data/ohare_jan.csv.

```{r}
flights <- read_csv(file = "https://nkha149.github.io/stat385-sp2020/files/data/ohare_jan.csv")
```

### Using `dplyr` and `ggplot2` together

- For this exercise, you will need to:
  - Graph a plot that can be used to answer the question.
  - Determine the type of plot that is needed.
  - (You might need to) Manipulate the data to get the specific information that you want.
  
- There are 2 parts to this exercise: each part worths 10 points.

- **(a)** How does the **average** departure delay time differ among days of the week?
```{r}

model1 = flights %>%
  group_by(DAY_OF_WEEK) %>%
  summarize(AVG_DEPARTURE_DELAY = mean(DEPARTURE_DELAY, na.rm = TRUE))

model1

ggplot(data = model1) +
  geom_point(mapping = aes(x = DAY_OF_WEEK, y = AVG_DEPARTURE_DELAY), color = "red", size = 3) +
  xlab("Days of the Week") +
  ylab("Average Departure Delay")

```    



$\rightarrow$ The average of the departure delay is the highest to the lowest in the following order : Day7 - Day1 - Day4 - Day2 - Day3 - Day5 - Day6.    


- **(b)** Airlines are grouped into different terminals. There is a belief that certain terminals have better taxing out time. How does **median** taxi out time differ among diferrent airlines?
```{r, warning = FALSE, message = FALSE}

library(gridExtra)

model2 = flights %>%
  select(AIRLINE, TAXI_OUT)

plot1 = ggplot(data = model2) +
  geom_boxplot(mapping = aes(x = AIRLINE, y = TAXI_OUT), color = "darkorange") +
  xlab("Airline") +
  ylab("Taxi Out Time")

model3 = flights %>%
  group_by(AIRLINE) %>%
  summarize(MED_TAXI_OUT = median(TAXI_OUT, na.rm = TRUE))

model3

plot2 = ggplot(data = model3) +
  geom_point(mapping = aes(x = AIRLINE, y = MED_TAXI_OUT), color = "red", size = 3) +
  xlab("Airline") +
  ylab("Median Taxi Out Time")

grid.arrange(plot1, plot2, nrow = 1)

```    



$\rightarrow$ Reflecting on the results from the box plots of the taxing out time and the scatter plot of the median of the taxing out time of each of the airlines, although not significantly different, we can clearly obtain the fact that 4 airlines: "AA", "EV", "MQ" and "NK" have a shorter taxing out time overall. Therefore, the belief that certain terminals have better taxing out time can be reasonable. However, we should have in mind that airline "MQ" has some outliers, which is insisting that the taxing out time can be extremely long for some rare incidents. 









